Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-05 Manuscript.Rmd
Working on a contrast permutation

      # relabel samples
      tempBig <- sample(bigSample)
      tempOne <- tempBig[1:lOne]
      tempTwo <- tempBig[(lOne+1):length(bigSample)]

@@

``` {r ROI computation, echo=FALSE, message = FALSE}

@@

>>>>

      # relabel samples
      tempBig <- sample(bigSample)
      tempOne <- tempBig[seq(lOne)]
      tempTwo <- tempBig[-seq(lOne)]

@@

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("_25_",
                "_OFC_",
                "_10v_",
                "_s32_",
                "_TE1a_",
                "_STSva_",
                "_8ad_",
                "_9p_",
                "_23d_",
                "_d23ab_",
                "_31a_",
                "_31pv_",
                "_31pd_",
                "_7m_",
                "_v23ab_",
                "_p24_",
                "_d32_",
                "_9m_",
                "_p32_",
                "_a24_",
                "_s32_",
                "_10r_",
                "_10d_",
                "_9a_",
                "_p10p_",
                "_PCV_",
                "_POS1_",
                "_RSC_")

Yeo_PCC_labels <- c("_7m_",
                    "_23d_",
                    "_31a_",
                    "_31pd_",
                    "_31pv_",
                    "_PCV_",
                    "_POS1_",
                    "_RSC_",
                    "_d23ab_",
                    "_v23ab_")

mPFC_only <- c("_a24_",
               "_d32_",
               "_p32_",
               "_10r_",
               "_9m_",
               "_10v_",
               "_OFC_",
               "_s32_",
               "_p24_")

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
setwd('./DEC')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F)

setwd('../DMN/')
templist <- dir()
studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)

# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 10
nullDist <- numeric()

for (i in seq(nPerms)) {

  # Sample all the studies and divide into 2 groups
  randPerm <- sample(allStudies)
  tmpSV <- randPerm[seq(length(studyList_sv))]
  tmpDMN <- randPerm[-seq(length(studyList_sv))]

  # Count the number of times each region was reported in the literature
  # Bilateral activations still count as 1, so we might want to reconsider that
  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))

  # Perform the prop test for each pair and get the max chi-squared stat
  nullDist[i] <- max(
                  apply(tmpDF[,2:3], 1, function(data) {
                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
                    }
                  ), na.rm = T)

}
```

``` {r ROI computation, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("_25_",
                "_OFC_",
                "_10v_",
                "_s32_",
                "_TE1a_",
                "_STSva_",
                "_8ad_",
                "_9p_",
                "_23d_",
                "_d23ab_",
                "_31a_",
                "_31pv_",
                "_31pd_",
                "_7m_",
                "_v23ab_",
                "_p24_",
                "_d32_",
                "_9m_",
                "_p32_",
                "_a24_",
                "_s32_",
                "_10r_",
                "_10d_",
                "_9a_",
                "_p10p_",
                "_PCV_",
                "_POS1_",
                "_RSC_")

Yeo_PCC_labels <- c("_7m_",
                    "_23d_",
                    "_31a_",
                    "_31pd_",
                    "_31pv_",
                    "_PCV_",
                    "_POS1_",
                    "_RSC_",
                    "_d23ab_",
                    "_v23ab_")

mPFC_only <- c("_a24_",
               "_d32_",
               "_p32_",
               "_10r_",
               "_9m_",
               "_10v_",
               "_OFC_",
               "_s32_",
               "_p24_")

@@

# Now select only the ROIs from Yeo et al (TEMP)
valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
